---
title: "Assignment 5 - Meta-analysis of pitch in schizophrenia"
author: "Riccardo Fusaroli"
date: "3/7/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

setwd("C:/Users/Bruger/Desktop/Programming/Semester 3/asm 8")

library(pacman)

p_load(dplyr, lme4, lmerTest, ggplot2, stringr, plyr, caret, modelr, ModelMetrics, tidyverse, MASS, simr, MuMIn, cvTools, hydroGOF, lsr, pastecs, crqa, dostats, readr, coda, languageR)




meta_data = read.csv("Data.csv", sep = ";")



#Collect all data to figure out if we have evidence for distict mean + sd, etc, for pitch in schizophrenia.
#A way of accounting for variance = weight = 1/variance --> the more variance you have, the bigger the confidence intervals. The less participants you have, the less the effect sizes counts.


# library(pacman)p_load(metafor)
# 
# PitchRange=escalc('SMD', n1i=ASD_N, n2i=TD_N, m1i=PitchRangeASD_Mean, m2i=PitchRangeTD_Mean, sd1i=PitchRangeASD_SD, sd2i=PitchRangeTD_SD, data = d)


# Model <- lmer(yi ~ 1 + (1 | study), weights = 1/vi, data=data, control=lmerControl(check.nobs.vs.nlev="ignore", check.nobs.vs.nRE="ignore")))
# Meta-analysis optimization:
# res <- rma(yi, vi, data = PitchRange, slab=Paper)
# Forest(res)
# 


# effect size = difference in the distributions

#esclc('smd', n1i = SampleSize_zcrtl, n2i = SS_sch) calculating choens d - the uncertanty, two additional column yi = cohens d, vi = variance.

#^ needed to put in here = lmerEffect size ~ 1 + (1|study), weights = 1/variance etc

#forrest plot: model_1 = rm2(yi, vi, data, slab = "study")
#forest(model_1)

```

# Building on the shoulders of giants: meta-analysis

## Questions to be answered

1. What is the current evidence for distinctive patterns of pitch mean and pitch sd in schizophrenia? Report how many papers report quantitative estimates, your method to analyze them, the estimated effect size of the difference (mean effect size and standard error for pitch mean, same for pitch sd) and forest plots representing it. 

2. Do the results match your own analysis from Assignment 3? If you add your results to the meta-analysis, do the estimated effect sizes change? Report the new estimates and the new forest plots.

3. Assess the quality of the literature: report and comment on heterogeneity of the studies (tau, I2), on publication bias (funnel plot), and on influential studies.

## Tips on the process to follow:

- Download the data on all published articles analyzing pitch in schizophrenia: https://www.dropbox.com/s/pmgw8wzc308so1p/Data.csv?dl=0
- Following the procedure in the slides calculate effect size and standard error of the effect size per each study. N.B. we focus on pitch mean and pitch standard deviation.
 . first try using lmer (to connect to what you know of mixed effects models)
 . then use rma() (to get some juicy additional statistics)
 
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(pacman)

p_load(metafor)

#Calculating Cohens D and variance (yi, vi) on Means

Pitch_Range = escalc('SMD', n1i=SampleSizeSchizo, n2i=SampleSizeContros, m1i=PitchMeanControls, m2i=PitchMeanSchizo, sd1i=PitchMeanControlsSD, sd2i=PitchMeanSchizoSD, data = meta_data)

#Calculating Cohens D and variance (yi2, vi2) on SDs

Pitch_Range_2 = escalc('SMD', n1i=SampleSizeSchizo, n2i=SampleSizeContros, m1i=PitchSDControls, m2i=PitchSDSchizo, sd1i=PitchSDControlsSD, sd2i=PitchSDSchizoSD, data = meta_data)

#changing column names to merge
colnames(Pitch_Range_2)[13] = "yi2"
colnames(Pitch_Range_2)[14] = "vi2"


#merge dataframes
pitch_range = merge(Pitch_Range, Pitch_Range_2)


# Model of the means

model_mean = lmer(yi ~ 1 + (1|Article), weights = 1/vi, data = pitch_range, control = lmerControl(check.nobs.vs.nlev = "ignore", check.nobs.vs.nRE = "ignore"))

summary(model_mean)


# Model of SD


model_SD = lmer(yi2 ~ 1 + (1|Article), weights = 1/vi2, data = pitch_range, control = lmerControl(check.nobs.vs.nlev = "ignore", check.nobs.vs.nRE = "ignore"))

summary(model_SD)




```

- Build a forest plot of the results (forest(model))

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#Forrest Plot
?rma()

Pitch_Range = Pitch_Range[complete.cases(Pitch_Range$yi), ]

f1 = rma(yi, vi, data = pitch_range, slab = Article)
summary(f1)

f2 = rma(yi2, vi2, data = pitch_range, slab = Article)
summary(f2)

forest(f1)
forest(f2)

```
 
- Go back to Assignment 3, add your own study to the data table, and re-run meta-analysis. Do the results change?

```{r setup, include=FALSE}

asm3data = read.csv("final_rqa.csv", header = T)

#Make a dataframe containing only controls mean + SD and schizo mean + sd


resultsDF = read.csv("final_rqa.csv")

SampleSizeSchizo = length(unique(asm3data$participant[asm3data$diagnosis == "schizophrenia"]))
SampleSizeContros = length(unique(asm3data$participant[asm3data$diagnosis == "control"]))
PitchMeanControls = mean(asm3data$mean[asm3data$diagnosis == "control"])
PitchMeanSchizo = mean(asm3data$mean[asm3data$diagnosis == "schizophrenia"])
PitchMeanControlsSD = sd(asm3data$mean[asm3data$diagnosis == "control"])
PitchMeanSchizoSD = sd(asm3data$mean[asm3data$diagnosis == "schizophrenia"])

PitchSDControls = mean(asm3data$stdDev[asm3data$diagnosis == "control"])
PitchSDSchizo = mean(asm3data$stdDev[asm3data$diagnosis == "schizophrenia"])
PitchSDControlsSD = sd(asm3data$stdDev[asm3data$diagnosis == "control"])
PitchSDSchizoSD = sd(asm3data$stdDev[asm3data$diagnosis == "schizophrenia"])
Article = "Assignment_3"
Year = 2017


asm3df = data.frame(Article, Year, SampleSizeSchizo, SampleSizeContros, PitchMeanControls, PitchMeanControlsSD, PitchMeanSchizo, PitchMeanSchizoSD, PitchSDControls, PitchSDControlsSD, PitchSDSchizo, PitchSDSchizoSD)

asm3 = rbind(meta_data, asm3df)

Pitch_mean_asm3 = escalc("SMD", n1i=SampleSizeSchizo, n2i=SampleSizeContros, m1i=PitchMeanSchizo, m2i=PitchMeanControls, sd1i=PitchMeanSchizoSD, sd2i=PitchMeanControlsSD, data = asm3)

Pitch_sd_asm3 = escalc("SMD", n1i=SampleSizeSchizo, n2i=SampleSizeContros, m1i=PitchSDSchizo, m2i=PitchSDControls, sd1i=PitchSDSchizoSD, sd2i=PitchSDControlsSD, data = asm3)

colnames(Pitch_sd_asm3)[13] = "yi2"
colnames(Pitch_sd_asm3)[14] = "vi2"

#model mean
model_mean_asm3 =  lmer(yi ~ 1 + (1 | Article), weights = 1/vi, data=Pitch_mean_asm3, control=lmerControl(check.nobs.vs.nlev="ignore", check.nobs.vs.nRE="ignore"))
summary(model_mean_asm3)

#model sd
model_sd_asm3 =  lmer(yi2 ~ 1 + (1 | Article), weights = 1/vi2, data=Pitch_sd_asm3, control=lmerControl(check.nobs.vs.nlev="ignore", check.nobs.vs.nRE="ignore"))
summary(model_sd_asm3)

#merging
pitch_range_asm3 = merge(Pitch_mean_asm3, Pitch_sd_asm3)


#Forest plot
#Pitch_mean_asm3 = Pitch_mean_asm3[complete.cases(Pitch_mean_asm3$yi), ]

f1 = rma(yi, vi, data = pitch_range_asm3, slab = Article)


f2 = rma(yi2, vi2, data = pitch_range_asm3, slab = Article)




```

- Now look at the output of rma() and check tau and I2

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#mean
summary(f1)
forest(f1)

#sd
summary(f2)
forest(f2)


#testing publication bias

#Influential studie 
inf = influence(f1)
print(inf)
plot(inf)

inf2 = influence(f2)
print(inf)
plot(inf)

#funnel plot
regtest(f1)
ranktest(f1)

regtest(f2)
ranktest(f2)



```
